---
title: "Developing Data Products"
author: "Shlomi Rosenberg"
date: "2018 M08 5"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview
This is an R Markdown presentation of my Developing Data Products course assignment.
In this assignment/Project, i have created a Shiny application which allows exploring cars horsepower (hp), cylinder count (cyl) and transmition type (am) on fuel consumption (mpg).


## Resources

###To check out the shiny exploration application, visit:
https://shrosenb.shinyapps.io/MyCarsShinyApp/

###For the source code (ui.R and server.R), visit:
https://github.com/shrosenb/DevelopingDataProductsAssignment4


## UI Code - MT Car Road Tests Data
```{r eval=FALSE, echo=TRUE, warning=FALSE}
shinyUI(fluidPage(
  
  sidebarLayout(
    sidebarPanel(
      h5(strong("Transmition Type:")),
      checkboxInput("am_a", "Automatic", value = TRUE),
      checkboxInput("am_m", "Manual", value = TRUE),
      h5(strong("Cylinder Count:")),
      checkboxInput("cyl_4", "4", value = TRUE),
      checkboxInput("cyl_6", "6", value = TRUE),
      checkboxInput("cyl_8", "8", value = TRUE),
      sliderInput("hp", "Engine HP Range:", min = 1, max = 200, value = 100)
    ),

    mainPanel(
       plotOutput("mpgPlot")
    )
  )
))
```

## Server Code - MT Car Road Tests Data
```{r eval=FALSE, echo=TRUE, warning=FALSE}
shinyServer(function(input, output) {
  output$mpgPlot <- renderPlot({
    # Transmition Auto/Manual
    ams <- 99
    if(input$am_a) {ams <- c(ams, 0)}
    if(input$am_m) {ams <- c(ams, 1)}
    # Number of cylinders
    cyls <- 99
    if(input$cyl_4) {cyls <- c(cyls, 4)}
    if(input$cyl_6) {cyls <- c(cyls, 6)}
    if(input$cyl_8) {cyls <- c(cyls, 8)}
    # Horse power
    hps  <- input$hp
    pData <- subset(mtcars, (am %in% ams) & (cyl %in% cyls) & ((hp >= hps[1]) & (hp <= hps[2])))
    pData$am <- factor(pData$am)
    # Plot
    p <- qplot(hp, mpg, data = pData, color = am, facets = am~cyl, main = "Scatterplots of MPG vs. Horsepower",
               xlab = "Horsepower", ylab = "Miles per Gallon")
    p <- p + geom_point(size = 3)
    p <- p + theme(axis.title = element_text(face = "bold.italic", size = "12", color = "brown"), 
                   legend.position = "top")
    p
  })
})
```



## Server Code (plot) - MT Car Road Tests Data
```{r warning=FALSE}
    library(ggplot2)
    mtcars$am <- factor(mtcars$am)
    p <- qplot(hp, mpg, data = mtcars, color = am, facets = am~cyl, xlab = "Horsepower", ylab = "Miles per Gallon")
    p <- p + geom_point(size = 3)
    p <- p + theme(axis.title = element_text(face = "bold.italic", size = "12", color = "brown"), 
                   legend.position = "top")
    p
```

